Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 introduction.tex
working, also spell checked

This situation can affect how data science teams; as analysts and
toolbuilders, we have experienced this first-hand in our environment, and
others report similar findings. Gutierrez collected interviews with data
scientists~\cite{Gutierrez:2014:DSA}, which include the following:

>>>>

This situation can affect how data science teams; as analysts and
tool builders, we have experienced this first-hand in our environment, and
others report similar findings. Gutierrez collected interviews with data
scientists~\cite{Gutierrez:2014:DSA}, which include the following:
